\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-31 manuscript.Rmd

# Descriptives
Descriptives <- psych::describe(LB)
alpha <- psych::alpha(LB)
Item.total <- alpha$item.stats
Item.total$r.cor
Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), apa(normality$statistic,2,T), apa(normality$p_value,2,F), apa(Item.total$r.cor,2,F))
colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics", "p", "Item-Total Correlation")
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(Des.combined) = (my.names)

#Polychoric Correlation matrix
LB.factor <- sapply(LB, as.factor)
correlations <- polychoric(LB.factor, correct = 0)

@@

# Item analysis
Item_analysis <- psych::alpha(LB)
Item_analysis$item.stats$r.cor
R.cor.sum <- summary(Item_analysis$item.stats$r.cor)
low.r.cor <- abs(R.cor.sum[1])
high.r.cor <- R.cor.sum[6]
```
Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].

@@

Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items. some of the items were skewed with high Kurtosis values. The Shapiro-Wilk test of normality [@shapiroAnalysisVarianceTest1965] indicated all the items violated normality assumptions. Multivariate normality assumptions were investigated by Marida's test [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis = `r printnum(mardia$b2p)` (p <0.001) indicated  multivariate normality assumptions violation. Due to these violations and ordinal nature of the response data  polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018]. Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA. However only `r apa(((BigR/totR)*100), 2,T)`% of the inter-item correlation coefficients were greater than .30 in the obtained matrix. The corrected item-total correlations ranged between `r apa(low.r.cor,2,F)` to `r apa(high.r.cor,2,F)`.

>>>>

# Descriptives
Descriptives <- psych::describe(LB)
alpha <- psych::alpha(LB)
Item.total <- alpha$item.stats

Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), apa(normality$statistic,2,T), apa(normality$p_value,2,F), apa(Item.total$r.cor,2,F))

colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics", "p", "Item-Total Correlation")

rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.names <- paste(rownameprefix,rownamesufix, sep = "" )

rownames(Des.combined) = (my.names)

#Polychoric Correlation matrix
LB.factor <- sapply(LB, as.factor)
correlations <- polychoric(LB.factor, correct = 0)
upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]

as.data.frame(upper)
min.cor <- abs(min(upper)) #minimum cor.coefficient of the matrix
max.cor <- abs(max(upper)) # max. correlation coefficent of the matrix

# Calulating the percentange of correlations higher than .30

@@

# Item analysis
Item_analysis <- psych::alpha(LB)
Item_analysis$item.stats$r.cor
R.cor.sum <- summary(Item_analysis$item.stats$r.cor)
low.r.corec <- abs(R.cor.sum[1])  #minimum item total correlation
high.r.corec <- R.cor.sum[6]     # maximum item total correlation
```

Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].

@@

```{r figCor,fig.cap= "Iter-correlation of the items",results='asis'}

qgraph(correlations$rho, cut =.30, details =T, posCol = "green", negCol = "orangered3", 
       labels = names(LB))
```

Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items. some of the items were skewed with high Kurtosis values. The Shapiro-Wilk test of normality [@shapiroAnalysisVarianceTest1965] indicated all the items violated normality assumptions. Multivariate normality assumptions were investigated by Marida's test [@mardiaMeasuresMultivariateSkewness1970]. Multivariate skew = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis = `r printnum(mardia$b2p)` (p <0.001) indicated  multivariate normality assumptions violation. Due to these violations and ordinal nature of the response data  polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018]. Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA. However only `r apa(((BigR/totR)*100), 2,T)`% of the inter-item correlation coefficients were greater than .30 in the obtained matrix. The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`. The corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
